\documentclass{resume}

\begin{document}

%\section{Summary of Qualifications}
\section{Education}
\begin{tabularx}{\textwidth}{rX}
  \textsc{Aug} 2016 - \textsc{Present} & \textbf{Mechanical Engineering \textbar} GPA 3.58/4.0\newline
  \textbf{Georgia Institute of Technology}, Atlanta, GA\newline
  Dean's List\newline
  2\textsuperscript{nd} Year Junior, Expected Graduation June 2020\\
  % \textsc{June} 2016 & \textbf{Milken Community High School}, Los Angeles, CA\newline
     % AP Courses: Calculus, Physics, Computer Science, Statistics, Chemistry, Biology\newline
     % Honors Roll\newline
     % National Honors Society\\
\end{tabularx}

\section{Academic Projects}
\experience{GT Motorsports}{Powertrain Team Member}{Aug 2016-Present}
Simulating engine dynamics with the eventual goal of increasing efficiency and low-end torque by lowering power-band. Designing and manufacturing improved camshaft to match optimal lift profile.

\experience{RoboJackets}{Team Member}{Aug 2016-Present}
Lead design of a 3lb combat robot to compete in the Motorama event, including CAD, chassis analysis, and weapon optimization. Manufacturing robotic mechanism components using precision machinery including CNC mills and lathes.

\experience{MilkenKnights FRC Team}{Team Captain}{Aug 2011-Jun 2016}
Managed the 6-week design and construction of a robot, including rapid prototyping, CAD, manufacturing, and control dynamics. Designed transmissions, gearboxes, chassis, and complex linkages in Solidworks. Implemented position PID, velocity PID, vision tracking, motion profiles, and path following. Trained students in CAD and operating precision machinery including a mill, lathe, and CNC router. Established sponsorship ties with local manufacturing businesses.

\experience{ASCE Bridge Building Team}{Team Captain}{Sept 2014-Jun 2016}
Lead design, analysis, simulation, and construction of a three foot, one pound popsicle stick bridge that withstood over 950 pounds of force.

%\experience{LADWP Science Bowl Team}{Team Captain}{Sept 2014-Jun 2016}
%Trained two teams of five people to participate in the annual LADWP science bowl competition.

\experience{Conrad Spirit of Innovation}{Programming/Electrical Lead}{Sept 2014-Jun 2015}
Designed, wired, and programmed LIDAR tracking system for a belt than warned the visually-impaired of threatening obstacles.

\experience{Edge Systems Design}{Mechanical Engineer}{Jun 2012-Jun 2014}
Designed base frame and linear motion system for an affordable CNC router targeted at the hobby market. Helped manage funding and operation of a startup.

\section{Technical Skills}
\begin{tabular}{rl}
  \textsc{Software:}   & Solidworks, Autodesk Inventor, Adobe Illustrator, Vim, Word, Excel\\
  \textsc{Manufacturing:}   & Haas CNC, Manual Mill, Manual Lathe, Laser Cutter, Waterjet, 3D Printer\\
  \textsc{Programming:}  & MatLab, Java, LabView, Arduino, HTML, CSS, SASS, Android, Python, \LaTeX\\
\end{tabular}

\section{Awards \& Honors}
\begin{tabular}{rll}
  \textsc{Nov} 2017 & 7\textsuperscript{th}/60 & Georgia Tech ME2110 Design Competition\\
  \textsc{Apr} 2016 & 2\textsuperscript{nd}/42 & FIRST Robotics Orange County Regional\\
  \textsc{Mar} 2015 & 3\textsuperscript{rd}/41 & FIRST Robotics Ventura Regional\\
  \textsc{Mar} 2015 & 3\textsuperscript{rd}/53 & FIRST Robotics Utah Regional\\
  \textsc{Oct} 2014 & International & Conrad Spirit of Innovation Semi-Finalist\\
  %\textsc{Mar} 2013 & 2\textsuperscript{nd}/26 & FIRST Madtown Robotics Off-season\\
  \textsc{Mar} 2013 & 1\textsuperscript{st}/65 & FIRST Robotics Los Angeles Regional\\
  %\textsc{Mar} 2012 & 2\textsuperscript{nd}/66 & FIRST Robotics Los Angeles Regional\\
\end{tabular}

\end{document}
