\documentclass[12pt]{cover_letter}

\date{April 11, 2018}

\usepackage{pdfpages}

\begin{document}
  \begin{letter}{}

    \opening{Dear Auris hiring manager,}

    % Sets the current page style to fancy (must happen after "opening")
    \thispagestyle{fancy}

    Your \textit{Mechanical Engineering Internship} posting found on the Auris Careers website interests me. A background on extra-curricular competition teams has given me extensive experience in 3D CAD, design for manufacture, and rapid prototyping, which would allow me to make meaningful contributions on your research and innovation design team.

    I was first exposed to CAD on a FIRST robotics team, where I performed various leadership rolls including CAD, engineering, and eventually team captain. Working with professional machine shops honed my ability to create unambiguous engineering drawings while the short, six-week build period taught me efficient design. And, in the confines of a short, six-week build period, I improved my ability to rapidly ideate and design for ease of manufacture. In particular, I became particularly adept in both designing for and manufacturing with our in-house manual and CNC equipment. By my senior year, I managed our prototyping team, utilizing CNC routed wood to go from problem, to idea, to manufacturing, to functioning concept in under twenty-four hours. My skills would be invaluable to your team, where I could help create easy-to-manufature proofs of concept.

    My work at Georgia Tech has cemented my desire to use engineering principles to solve challenging problems. After I took Dynamics and Numerical Methods at GT, I wrote robotic path planning and motion control algorithms for autonomous robots. In the past year, I lead a team of six students in designing and manufacturing a three pound battlebot. The team extensively used FEA to optimize the chassis and weapon performance for their weight. I believe I would thrive on your collaborative, multi-disciplinary team where I would be challenged on a daily basis.

    Attached you will find my resume; it contains further descriptions of my work on Georgia Tech's FSAE and robotics teams and my high school robotics team. I would be happy to answer further questions by email at \href{mailto:michael.bick@gatech.edu}{\nolinkurl{michael.bick@gatech.edu}}.

    \closing{Sincerely,}

  \end{letter}
\end{document}
