\documentclass[12pt]{cover_letter}

\date{April 9, 2018}

\usepackage{pdfpages}

\begin{document}
  \begin{letter}{}

    \opening{Dear Haas hiring manager,}

    % Sets the current page style to fancy (must happen after "opening")
    \thispagestyle{fancy}

    Your \textit{Mechanical Engineering Internship} posting found on the Haas Careers website interests me. A background on extra-curricular competition teams has given me extensive experience in 3D CAD, machining, and lean manufacturing which would allow me to make meaningful contributions on your engineering team.

    I was first exposed to machine tools on a FIRST robotics team, where I performed various leadership rolls including CAD, engineering, and eventually team captain. In order to maximize productivity in the short, six-week build period, I implemented lean principles. In particular, I created standardization procedures to minimize waste and created a spreadsheet to track the production of parts. I also became particularly adept in both designing parts for and manufacturing with our in-house manual mill, manual lathe, and Haas CNC router. By my senior year, the team would design, manufacture, and test new prototypes in a day's time. I would fit into your team, where my skills in improving quality and productivity could be vitally used.

    My work at Georgia Tech has cemented my desire to use engineering principles to solve challenging problems. In the past year, I lead a team of six students in designing and manufacturing a three pound battlebot. The team extensively used FEA to optimize the chassis and weapon performance for their weight. I also developed my manufacturing skills, machining complex, 3D parts for the GT Formula SAE team. I believe I would thrive on your collaborative, multi-disciplinary team where I would be challenged on a daily basis.

    Attached you will find my resume; it contains further descriptions of my work on Georgia Tech's FSAE and robotics teams and my high school robotics team. I would be happy to answer further questions by email at \href{mailto:michael.bick@gatech.edu}{\nolinkurl{michael.bick@gatech.edu}}.

    \closing{Sincerely,}

  \end{letter}
\end{document}
