\documentclass[12pt]{cover_letter}

\date{February 2, 2019}

\usepackage{pdfpages}

\begin{document}
  \begin{letter}{}

    \opening{Dear Haas hiring manager,}

    % Sets the current page style to fancy (must happen after "opening")
    \thispagestyle{fancy}

    Your \textit{Mechanical Engineering Internship} posting found on the Haas Careers website interests me. A background on extra-curricular competition teams has given me extensive experience in 3D CAD, machining, and lean manufacturing which would allow me to make meaningful contributions on your engineering team.

    At Georgia Tech, I have lead a team in building a robot that competed in the Georgia Tech "Creative Design Decisions Competition". The team prioritized building quick, useful iterations -- a methodology similar to the concept of Agile Development in computer science -- in order to learn about and fix failures quickly. By taking advantage of CAD, laser cutters, and 3D printers, the team iterated through three major robot revisions in the same amount of time in which most teams only worked on one.

    In the past, I also lead a team of six students in designing and manufacturing a three pound battlebot. The team extensively used CNC machining to create a novel weapon drum that was more reliable and powerful than the equivalent drum manufactured with conventional machining methods. In high school I served as engineering and team captain of my FIRST robotics team. In order to maximize productivity in the short, six-week build period, I implemented lean principles. In particular, I created standardization procedures to minimize waste, created a production tracking system that reduced manufacturing mistakes, and implemented a kanban inventory system.

    Attached you will find my resume; it contains further descriptions of my work on various engineering teams at Georgia Tech and since high school. I would be happy to answer further questions by email at \href{mailto:michael.bick@gatech.edu}{\nolinkurl{michael.bick@gatech.edu}}.

    \closing{Sincerely,}

  \end{letter}
\end{document}
